Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-03 draft/draft.tex
progress

\section{
Data
\label{sec:data}
}

The data comprehends 5 soccer leagues from England, France, Germany, Italy and Spain.
Each has 20 teams, with the exception of Germany which has 18.
For each pair of teams $i$ and $j$ of a given league, a score $\phi_{ij}\in \RR$ is provided, which is the aggregate of the two games between them, one as a local and another as a visitor.
There are ten different types of scores:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:}
\end{enumerate}

>>>>

\section{
Methods
\label{sec:methods}
}

\subsection{
Data
\label{sec:data}
}

The dataset covers five soccer leagues: England, France, Germany, Italy, and Spain.
Each league consists of 20 teams, except for Germany, which has 18.
Every pair of teams $i,j$ plays two matches: one with $i$ as the home team and $j$ as the away team, and in the other match it is the other way around.
The teams are indexed or ranked according to their position in that year’s final standings.
The standings is characterized by some tournament points $\pi_i$ for each team $i$ in each league.
Therefore, the condition $i<j$ holds if and only if $\pi_i>\pi_j$ for any two teams $i$ and $j$ in a given league.

For each pair of teams $i$ and $j$ in a given league, several pairwise metrics $m_{ij}\in \mathbb{R}$ are provided.
Each metric takes a positive value if it presumably favors team $i$ over team $j$, and a negative value otherwise.
The different types of empirically determined metrics being considered are:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:} bla bla.
\end{enumerate}
Namely, $m_{ij}$ corresponds to $i$ being the home team and $j$ being the away team.
Additionally, metric-styles derived from the Singular Value Decomposition of previous metrics are also considered~\cite{chacoma2025data}.
Moreover, in order to test the inference of ratings, two types of ground-truth metrics are also defined.
Namely, the rank-based metric $m_{ij}=\frac{1}{2}(i-j)$ and the tournament point metric $m_{ij}=\frac{1}{2}(\sigma_j-\sigma_i)$.
Notice, $m_{ij}$ is generally independent of the metric $m_{ji}$ since they belong to different matches between $i$ and $j$.
In the case of the ground-truth metrics, it holds that $m_{ij}=-m_{ji}$.

{\color{red}[HERE...]}
